A recipe for extremely reproducible enrichment analysis (and why we need it)

### 2023-12-05 manuscript/manuscript.Rmd
Update manuscript.Rmd
Update manuscript.Rmd
PMC6381667 changes - DAVID and IPA

| 3.PMC6381667: Figure 1 and Figure 2 | A. Results are not reproducible and are highly inconsistent B. N.A. | **2 (medium).** GO terms obtained after replication showed inconsistent results compared to the results in the original article. KEGG results were similar. Better naming convention for supplementary file for 117 genes for DAVID input is necessary. GO Results are not reproducible and are highly inconsistent. |

>>>>

| 3.PMC6381667: Figure 1 and Figure 2 | A. Results are not reproducible and are highly inconsistent B. N.A. | **2 (medium).** GO terms obtained after replication showed inconsistent results compared to the results in the original article. KEGG results were similar. Better naming convention for supplementary file for 117 genes for DAVID input is necessary. The paper mentions pathway analysis was done using  Ingenuity Pathway Analysis (IPA). Even DAVID provides pathway enrichment results. It is unclear which figures and results were obtained from either of the tools. Figures should have mentioned the name of the tools to avoid confusion for source of results.|
